Clean spectral data

### 2020-11-09 R/clean_spectral_data.Rmd
changed color of hist and spectra plot
and adjusted the histogram size to make it fit on one page for the figures section

# plot histogram with count per genusSpecies. color bars based on whether
# # samples exceeds the threshold
ggplot(taxonCounts, aes(y = reorder(genusSpecies, n), x = n)) + 
                          #reorder(taxonID, n), x = n)) + 
  geom_bar(stat = "identity", aes(fill = countGT)) + 
  labs(title = paste("Histogram of samples per species.",
                     speciesCountTotal, "total species;",
                     speciesCountGT, "species with greater than",
                     thresh, "samples"),
       y = "Scientific Name (Genus + Species)",
       fill = paste("Count >", thresh)) + 
  theme_bw() + 
  scale_fill_manual(values = c("#d95f0e", "#7bccc4"))
```
Histogram using scientific name

@@

@@

ggplot(distinct(taxons_GT, genusSpecies, .keep_all=TRUE), 
       aes(y = reorder(taxonID, n), x = n)) + 
  geom_bar(stat = "identity", fill = "#7E9E8F") + 
  labs(y = "Taxon code\n",
       x = "\nNumber of spectra") + 
  #theme(axis.text = element_text(size = 12)) +
  theme_bw(base_size=14)

# save figure to file
ggsave(filename = here::here("analysis","figures", "hist_samples_per_species.pdf"), width = 8, height = 9)
```

@@

Visualize the spectra, facet by scientific name, color by taxon rank. 
```{r, eval = FALSE, include = "FALSE", warning=FALSE, fig.height=12, fig.width=16}
filtered_spectra %>%
  ggplot(aes(wavelength_nm, ifelse(mask, NA, reflectance), group = spectraID,
             # color each facet plot based on taxonRank
             color = taxonRank)) +
  geom_path(alpha = .2) +
  labs(x = '\n Wavelength (nm)',
       y = 'Reflectance \n',
       color = "Taxon Rank") + 
  facet_wrap(~genusSpecies
             # wrap long scientific names
             ,labeller = label_wrap_gen(20)
             ,ncol=10) + 
  scale_color_manual(values = c("#e6550d","#1c9099", "#a8ddb5")) + 
  theme_minimal() + 
  # Adjust the text size and rotation angle 
  theme(text = element_text(size=11),
        axis.text.x = element_text(angle=90, hjust=1),
        axis.title.y = element_text(size = 14),
        axis.title.x = element_text(size = 14),
        legend.text = element_text(size = 14),
        legend.title = element_text(size = 14))
```

@@

```{r, warning=FALSE, fig.height=8, fig.width=10}
filtered_spectra %>%
  ggplot(aes(wavelength_nm, ifelse(mask, NA, reflectance), group = spectraID)) +
  geom_path(alpha = .2, color = "#1c9099") +
  labs(x = '\n Wavelength (nm)',
       y = 'Reflectance \n') + 
  facet_wrap(~genusSpecies
             # wrap long scientific names
             ,labeller = label_wrap_gen(20)
             ,ncol=5) +
  theme_minimal() + 
  # Adjust the text size and rotation angle 
  theme(text = element_text(size=11),
        axis.text.x = element_text(angle=90, hjust=1),
        axis.title.y = element_text(size = 14),
        axis.title.x = element_text(size = 14))

@@

Color the spectra by the year they were collected?

```{r, eval=FALSE, include=FALSE}
filtered_spectra %>%
  ggplot(aes(wavelength_nm, ifelse(mask, NA, reflectance), group = spectraID, color = as.factor(year))) +
  geom_path(alpha = .2) +
  labs(x = '\n Wavelength (nm)',
       y = 'Reflectance \n',
       color = "Year collected") + 
  facet_wrap(~genusSpecies
             # wrap long scientific names
             ,labeller = label_wrap_gen(20)
             ,ncol=10) + 
  scale_color_manual(values = c("#e6550d","#1c9099", "#a8ddb5")) + 
  theme_minimal() + 
  # Adjust the text size and rotation angle 
  theme(text = element_text(size=11),
        axis.text.x = element_text(angle=90, hjust=1),
        axis.title.y = element_text(size = 14),
        axis.title.x = element_text(size = 14),
        legend.text = element_text(size = 14),
        legend.title = element_text(size = 14))
```

>>>>

# plot histogram with count per genusSpecies. color bars based on whether
# # samples exceeds the threshold
ggplot(taxonCounts, aes(y = reorder(genusSpecies, n), x = n)) + 
                          #reorder(taxonID, n), x = n)) + 
  geom_bar(stat = "identity", aes(fill = countGT)) + 
  labs(title = paste("Histogram of samples per species.",
                     speciesCountTotal, "total species;",
                     speciesCountGT, "species with greater than",
                     thresh, "samples"),
       y = "Scientific Name (Genus + Species)",
       fill = paste("Count >", thresh)) + 
  theme_bw() + 
  scale_fill_manual(values = c("#36454f", "#7E9E8F"))
```
Histogram using scientific name

@@

# save figure to file
#ggsave(filename = here::here("analysis","figures", "hist_samples_per_species.pdf"), width = 9, height = 9)
```

@@

ggplot(distinct(taxons_GT, genusSpecies, .keep_all=TRUE), 
       aes(y = reorder(taxonID, n), x = n)) + 
  geom_bar(stat = "identity", fill = "#36454f") + 
  labs(y = "Taxon code\n",
       x = "\nNumber of spectra") + 
  #theme(axis.text = element_text(size = 12)) +
  theme_bw(base_size=14)

@@

@@

```{r, warning=FALSE, fig.height=8, fig.width=10}
filtered_spectra %>%
  ggplot(aes(wavelength_nm, ifelse(mask, NA, reflectance), group = spectraID)) +
  geom_path(alpha = .2, color = "#36454f") +
  labs(x = '\n Wavelength (nm)',
       y = 'Reflectance \n') + 
  facet_wrap(~genusSpecies
             # wrap long scientific names
             ,labeller = label_wrap_gen(20)
             ,ncol=5) +
  theme_minimal() + 
  # Adjust the text size and rotation angle 
  theme(text = element_text(size=11),
        axis.text.x = element_text(angle=90, hjust=1),
        axis.title.y = element_text(size = 14),
        axis.title.x = element_text(size = 14))

@@
